HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-20 LaTeX/ms.tex
Moved figures
Figures must be in same directory as latex file for ApJ submission.

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{../Figures/spirecolflux.pdf}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HELAISS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM31_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM29_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM07_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM20_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM01_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM09_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM11_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM23_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM22_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM05_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM30_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM12_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS12_870_500.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS04_870_500.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS13_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS11_870_500.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS10_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS01_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS09_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS08_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS01_870_250.pdf}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_residual_bestfit.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_residual_bestfit.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.195\textwidth]{../Figures/HECDFS04_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/HCOSMOS02_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/HELAISS02_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/HXMM11_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/HXMM20_rgb.pdf}
\end{centering}

@@

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{../Figures/f870_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/reff_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/offset_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/q_delens.pdf}

@@

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{../Figures/fluxtotalcomponent.pdf}

@@

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[height=3in]{../Figures/AllPositions.pdf}
\includegraphics[height=3in]{../Figures/dNdA.pdf}

@@

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=0.335\textwidth]{../Figures/DifferentialNumberCounts.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/s870_mu_z1p5.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/Pmu_S870_z1p5.pdf}

>>>>

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{spirecolflux.pdf}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{HELAISS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM31_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM29_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM07_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM20_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM01_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM09_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM11_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM23_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{HXMM22_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM05_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM30_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HXMM12_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HECDFS12_870_500.pdf}
\includegraphics[width=0.331\textwidth]{HECDFS04_870_500.pdf}
\includegraphics[width=0.331\textwidth]{HECDFS13_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HADFS04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HADFS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HADFS11_870_500.pdf}
\includegraphics[width=0.331\textwidth]{HADFS10_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HADFS01_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
\includegraphics[width=0.331\textwidth]{HADFS09_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HADFS08_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HADFS03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HCOSMOS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{HCOSMOS01_870_250.pdf}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.162\textwidth]{HELAISS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HELAISS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HELAISS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM31_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM31_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM31_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM29_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM29_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM29_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM07_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM07_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM07_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM20_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM20_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM20_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM09_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM09_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM09_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM11_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM11_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM11_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM23_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM23_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM23_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM22_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM22_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM22_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM05_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM05_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM05_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM30_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM30_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM30_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM12_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM12_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HXMM12_residual_bestfit.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
\includegraphics[width=0.162\textwidth]{HECDFS12_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS12_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS12_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS13_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS13_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HECDFS13_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS11_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS11_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS11_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS10_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS10_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS10_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS09_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS09_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS09_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS08_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS08_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS08_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HADFS03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HCOSMOS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HCOSMOS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HCOSMOS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HCOSMOS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HCOSMOS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{HCOSMOS01_residual_bestfit.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.195\textwidth]{HECDFS04_rgb.pdf}
\includegraphics[width=0.195\textwidth]{HCOSMOS02_rgb.pdf}
\includegraphics[width=0.195\textwidth]{HELAISS02_rgb.pdf}
\includegraphics[width=0.195\textwidth]{HXMM11_rgb.pdf}
\includegraphics[width=0.195\textwidth]{HXMM20_rgb.pdf}
\end{centering}

@@

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{f870_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/reff_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/offset_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/q_delens.pdf}

@@

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{fluxtotalcomponent.pdf}

@@

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[height=3in]{AllPositions.pdf}
\includegraphics[height=3in]{dNdA.pdf}

@@

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=0.335\textwidth]{DifferentialNumberCounts.pdf}
\includegraphics[width=0.335\textwidth]{s870_mu_z1p5.pdf}
\includegraphics[width=0.335\textwidth]{Pmu_S870_z1p5.pdf}
